Network Analysis of Code Similarity

### 2014-11-21 network-analysis.Rmd
Basic network graph

```{r echo=FALSE}
packrat::on()
library(magrittr)
library(RWeka)
library(stringi)
source("R/helper.R")

@@

```{r}
cf <- outer_for_lists(codes, codes, compare_codes_by_shared_ngrams)
diag(cf) <- NA   # remove codes compared to themselves
```

>>>>

```{r echo=FALSE}
packrat::on()
library(magrittr)
library(RWeka)
library(stringi)
library(igraph)
source("R/helper.R")

@@

```{r}
cf <- outer_for_lists(codes, codes, compare_codes_by_shared_ngrams)
```

Remove obviously incorrect values:

```{r}
cf2  <- cf
diag(cf2) <- NA                 # remove codes compared to themselves
cf2 <- rm_anachronism(cf2)       # remove anachronistic comparisons

significance_threshold <- 0.15
cf2[cf2 < significance_threshold] <- NA
cf2[is.na(cf2)] <- 0
```

Now we can create a graph object from the comparison matrix, which we will treat as an adjacency matrix.

```{r}
g <- graph.adjacency(cf2, mode = "directed", weighted = TRUE, diag = FALSE) 
set.seed(4821)
l <- layout.fruchterman.reingold(g, weights = E(g)$weight)
par(mar=c(0,0,0,0))
plot(g, edge.width = E(g)$weight * 12, layout = l, edge.arrow.size= 0.25, vertex.size = 5)
```
